### 2013-06-24 Tex/chapters/model.tex
Erläuterung zu finite size effects

    of the disordered Ising model in dependece of the disorder parameter
    \(\sigma\). At \(T_c\) the magnetisation \(|m|\) of the system will
    jump and the susceptibility \(\chi_m = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
    will diverge. But this behaivior is only present in infinite systems,
    hence every computer simulation will show some \emph{finte size effects}.
    Because of this all through computer simulations observed phase
    transitions will be "smeared out".
    [todo: Bezug zum Bild]

@@

        \subfigure[todo][]

@@

        \subfigure[todo][]

@@

        \caption[]
            todo

@@

>>>>

    of the disordered Ising model in dependence of the disorder parameter
    \(\sigma\). At \(T_c\) the mean absolute magnetisation \(\avg{|m|}\) of
    the system will jump and the susceptibility
    \(\chi = \frac{N}{T}\brac{\avg{m^2}-\avg{m}^2}\)
    will diverge. In fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}
    it is easy to see that the jump occurs at lower temperatures \(T\) for higher
    disorder parameters \(\sigma\) (here with a Relative Neighborhood graph).

@@

        \subfigure[Dependence of the phase transition on $\sigma$][]
        \subfigure[Example for finite size effects][]

@@

        \caption[Phase Transition and Finite Size Effects]

@@

            \subref{sfig:smeared_out:meanM_L}: Effects of the disorder
            parameter $\sigma$ on the phase transition
            for an underlying Relative Neighborhood graph with $L=128$.\\
            \subref{sfig:smeared_out:meanM}: Effects of different system
            sizes at \(\sigma = 0\). Dotted lines are guides to the eye.

@@

    But it is also visible, that there occurs no real jump, but a continuous
    decline. The jump is only present in infinite systems, hence every
    computer simulation will show some \emph{finte size effects}.
    These finite size effects cause a "smearing out" of the phase
    trasition. This is stronger for smaller system sizes, as showed in
    fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}.\\
